Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over \cye{convex domains and} domains with shellable triangulations

### 2024-09-27 main.tex
triangulation shape measure; scalar potential over triangulations; some macros

\usepackage{comment}          % 
\usepackage{hyperref}         % For hypertext links
\usepackage{tikz-3dplot}      % 3d plots

@@

\usepackage{enumitem}
\setitemize[1]{left=0.0cm}

@@

% Theorem environments

\newcommand{\mwl}[1]{\color{red}{MWL: #1}}
\newcommand{\notice}[1]{\color{red}{REMARK: #1}}
\newcommand{\disk}{\cye{ball}}

@@

Shellable triangulations are defined by a special constructive property:
we can assemble such triangulations sequentially, adding one simplex after another, such that the interface between the previous intermediate triangulation and the next simplex is always a boundary submanifold of both.
Loosely speaking, this guarantees that the interface with each successive simplex is sufficiently well-behaved.
Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler2012lectures}, which we only employ in a simple special case. 
In particular, local stars in 2D and 3D triangulations are shellable. 
\\

% This construction of potentials requires triangulations with special conditions: 
% we assemble the triangulation sequentially, adding one simplex after another, such that the interface between the previous intermediate triangulation and the next simplex is always a boundary submanifold of both.  Loosely speaking, this guarantees that the interface with each successive simplex is sufficiently well-behaved. Such triangulations are called \textit{shellable}. Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler2012lectures}, which we only employ in a simple special case. 
% In particular, local stars in 2D and 3D triangulations are shellable. 
% \\

@@

Whenever $\calT$ is a simplicial complex, 
the set of $k$-dimensional simplices in $\calT$ is denoted as $\subsimplex_{{k}}(\calT)$. 
% Additionally, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Edges(\calT) := \subsimplex_{1}(\calT)$ refer to the vertices and edges of the simplicial complex, respectively. In practice, we not always distinguish between points and singleton simplices. 
% Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces (that is, codimension one members) of this triangulation.\footnote{
Similarly, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ refer to the vertices and the faces (that is, codimension one members) of this triangulation.\footnote{
% \begin{remark}
    Our use of the term \textit{face} as is common in the finite element literature~\cite{brenner2008mathematical}
    and is synonymous with \textit{facet} as used in the literature on polyhedral combinatorics~\cite{schrijver1998theory}.
    Notably, this terminology differs from the uses \textit{face} and \textit{facet} in the theory of polyhedra~\cite{ziegler2012lectures}.
% \end{remark}
}
% Given $T \in \calT$, we let $\supsimplex(\calT,T)$ be the set of simplices in $\calT$ that contain $T$,
% and we write $\supsimplex_{k}(\calT,T)$ for the set of $k$-dimensional simplices in $\supsimplex(\calT,T)$.\footnote{\mwl{MWL: It might be more economical to get rid of the supersimplex set, it is only used in this section to define patches.}}

@@

Given a matrix $A \in \bbR^{n \times n}$, we let $\sigma_{1}(A) \geq \dots \geq \sigma_{n}(A) \geq 0$ denote the descending sequence of its singular values, 
where $\sigma_{\max}(A) := \sigma_{1}(A)$ is the largest and $\sigma_{\min}(A) := \sigma_{n}(A)$ is the smallest. 
We recall that the $\ell^{2}$ operator norm of $\|A\|_{2}$ agrees with $\sigma_{\max}(A)$,
and if $A$ is invertible, then $\|A^{-1}\| = \sigma_{\min}(A)^{-1}$.
% Another norm on matrices, less common but useful for us, is the \emph{maximum column norm} $\|A\|_{\maxcol}$, which is defined as the largest $\ell^{2}$-norm of any column of $A$.

Whenever $T$ is any $n$-dimensional simplex $T$,
we define the \textit{geometric shape measure} $\geometricshapemeasure(T)$,
the \textit{aspect shape measure} $\aspectratio(T)$,
and 
the \textit{algebraic shape measure} $\algebraicshapemeasure(T)$
by 
\begin{align}\label{math:shapemeasure}
    \geometricshapemeasure(T)
    := 
    \frac{ \diam(T)^{n} }{ n! \vol(T) }
    ,
    \qquad 
    \aspectratio(T)
    := 
    \frac{ \diam(T) }{ \height(T) }
    ,
    \qquad 
    \algebraicshapemeasure(T)
    := 
    \sup_{ \varphi : \Delta^n \rightarrow T } 
    \frac{ \sigma_{\max}( \Jacobian \varphi ) }{ \sigma_{\min}( \Jacobian \varphi ) }
%     \sup_{ \varphi : \Delta^n \rightarrow T } \| \Jacobian \varphi \|_{\maxcol} \| \Jacobian \varphi^{-1} \|_{\maxcol}
    ,
\end{align}
where the last supremum is taken over all affine transformation from the reference $n$-simplex onto the $n$-simplex $T$. 
% DONE: Although this is fairly clear upon reading, we could specify in word that $\geometricshapemeasure(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\volumeratio(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.

@@

We gather a few relationships between geometric and algebraic entities and compare the different shape measures.

\begin{lemma}\label{lemma:measurerelationships}
    Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism from the reference $n$-simplex. Then 
    \begin{gather*}
        \| \Jacobian \varphi \|
        \leq 
        \Ceins{n} \cdot \diam(T) % DONE: can this improved?
        ,
        \qquad 
        \| \Jacobian \varphi^{-1} \|
        \leq 
        \Czwei{n} \cdot 
        \geometricshapemeasure(T) 
        \diam(T)^{-1}
        ,
        \\
        \algebraicshapemeasure(T)
        \leq 
        \Cdrei{n}
        % \sqrt{ \frac{n}{ (n-1)^{n-1} } }
        \geometricshapemeasure(T)
        ,
        \qquad 
        %         \geometricshapemeasure(T)^{\frac 1 n}
        %         \leq 
        \aspectratio(T)
        \leq 
        \geometricshapemeasure(T)
        .
    \end{gather*}
    Here,
    \begin{align*}
        \Ceins{n} \leq \sqrt{n},
        \quad 
        \Czwei{n} \leq          \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}, 
        \quad 
        \Cdrei{n} \leq \Ceins{n}\Czwei{n} %\sqrt{n} \left( \frac{n}{n-1} \right)^{\frac{n-1}{2}}
        . 
    \end{align*}
\end{lemma}
\begin{proof}
%     The columns of the matrix $\Jacobian \varphi^{-1}$ are the gradients of the barycentric coordinates of the vertices of $T$,
%     except for the vertex $\varphi(0)$. It immediately follows that 
%     \begin{align*}
%         \| \Jacobian \varphi^{-1} \|_{2} \leq \sqrt{n} \cdot \height(T)^{-1}
%         .
%     \end{align*}
%     The smallest height in the reference simplex $\Delta^{n}$ is $1/\sqrt{n}$. 
%     
    We easily verify the first inequality. To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of the Jacobian $\Jacobian\varphi$ in descending order.
    The Jacobian determinant is the product of these singular values. 
    By a result of Hong and Pan \cite{hong1992lower},
    \begin{align*}
        \sigma_{n}
        &\geq 
        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
        \frac{ \det(\Jacobian\varphi) }{ \diam(T)^{n-1} }
        = 
        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
        \frac{ n! \vol(T) }{ \diam(T)^{n-1} }
        .
    \end{align*}
%     To get the second inequality, we multiple the last term by $\sigma_{1} / ( \sqrt{n} \diam(T) ) \leq 1$.
    The second inequality follows by taking the reciprocal. 
    The definition of the condition number now gives the third inequalities. 
    % To get the third inequality, we divide both sides by $\sigma_{1}$ and use $\sigma_{1} \leq \sqrt{n} \diam(T)$.
    Finally, 
    if $F$ is the face of $T$ opposite to the vertex with the smallest height, then 
    \begin{align*}
        \frac{ \diam(T) }{ \height(T) }
        \leq 
        \frac{ \diam(T) \vol(F) }{ n \vol(T) }
        \leq 
        \frac{ \diam(T)^{n} }{ n! \vol(T) }
        .
    \end{align*}
%     Since $n! \vol(T)$ is bounded from below by the product of any $n$ different heights of $T$, it follows that 
%     \begin{align*}
%         \frac{ \diam(T)^{n} }{ n! \vol(T) }
%         \leq 
%         \frac{ \diam(T)^{n} }{ \height(T)^{n} }
%         .
%     \end{align*}
    That shows the fourth and last of the inequalities. 
\end{proof}

@@

% Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^{n} / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
    % We can also rescale that by a factor of $1/n!$, as suggested from the above. 
    The geometric ratio $\geometricshapemeasure(T)$ equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}. 
    The \emph{thickness} of a simplex is the ratio of its smallest height to its diameter~\cite{munkres2016elementary}.
    Alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices.
    One example, commonly referenced in finite element literature, is the ratio of the diameter and the radius of the largest inscribed circle of a simplex 
% TODO     (see~\cite[p.61, Definition 5.1]{braess2001finite}, ~\cite[p.97, Definition (4.2.16)]{brenner2008mathematical},~\cite[Definition~11.2]{ern2021finite}). 
\end{remark}

We are interested in the maximal ratio of volumes between neighboring $n$-simplices, written $\volumeratio(\calT)$,
and the ratio of intersecting simplices, written $\diameterratio(\calT)$. Formally, 
\begin{align}
    \volumeratio(\calT) 
    := 
    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } 
    \frac{ \vol(T) }{ \vol(T') }
    ,
    \qquad 
    \diameterratio(\calT) 
    := 
    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \neq \emptyset } }
    \frac{ \diam(T) }{ \diam(T') }
    .
\end{align}
Whenever $T, T'$ are two $n$-simplices that share a common face $F$ of codimension $1$, we let $\Xi_{T,T'} : T \rightarrow T'$ denote the affine diffeomorphism 
that preserves $F$. We define 
\begin{align}\label{math:reflectionmeasure}
    \reflectionestimate(\calT) 
    := 
    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } }
    \| \Jacobian \Xi_{T,T'} \|
\end{align}
to be the maximum of the operator norm of the Jacobian of any such diffeomorphism. 
This indicator quantifies how much reflection across the shared face distorts the geometry.

@@

\begin{lemma}\label{lemma:volumecomparison}
    Let $T_1$ and $T_2$ be two $n$-simplices that share a common face $F$. Then 
    \begin{align*}
        \diam(T_1)
        \leq 
        % \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
        % \diam(F)
        % = 
        \geometricshapemeasure(T_1)
        \diam(F)
        ,
        \qquad 
        \frac{ \vol(T_1) }{ \vol(T_2) }
        \leq 
        % \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
        % \cdot 
        % \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
        % = 
        \aspectratio(T_1) \aspectratio(T_2)
        .
    \end{align*}
    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism that is the identity over $F$, then 
    \begin{align*}
        \| \Jacobian \Xi \|
        \leq 
        ( 1 + \aspectratio(T_2) ) \aspectratio(T_1)
        % \Cvier{n} \geometricshapemeasure(T_2) \geometricshapemeasure(T_1) 
        .
    \end{align*}
%     Here, $\Cvier{n} \leq \Ceins{n} \Czwei{n}$. 
\end{lemma}

@@

        \| \Jacobian \Xi \|
        \| \Jacobian\phi_{2} \| \cdot \| \Jacobian\phi_{1}^{-1} \|

@@

%         \| \Jacobian \Xi \|

@@

        \| \Jacobian \Xi \|

@@

\begin{remark}
    Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\volumeratio(\calT)$ but not $\diameterratio(\calT)$. 
    As seen above, we can bound the ratio of diameters and volumes of simplices that share at least one edge in terms of the shape measure. 
    If we have an upper estimate for the number of simplices sharing a given vertex, 
    we can also bound the ratios of diameters and volumes of simplices sharing only a single common vertex. 
\end{remark}
%%%%%%%% END HERE

@@

@@

\begin{lemma}\label{lemma:poincarefriedrichsoverfacepatch}
    Let $\calT$ be a triangulation.
    Let $T_{1}, T_{2} \in \calT$ be two $n$-simplices whose intersection is a common facet $F := T_1 \cap T_2$. 
    Write $U := T_1 \cup T_2$. 
    Then 
    \begin{align*}
        \min\limits_{ c \in \bbR }
        \| u - c \|_{L^{p}(U)}
        &
%         \leq 
%         2 C_{\PF,{\rm EFNT},p}
%         \max\left( 
%             \frac{ \vol(T_1) }{ \vol(T_2) }
%             ,
%             \frac{ \vol(T_2) }{ \vol(T_1) }
%         \right)^{\frac 1 p}
%         \\&\qquad\qquad 
%         \cdot 
%         \max\left( \diam(T_1), \diam(T_2) \right)
%         \| \nabla u \|_{L^{p}(U)}
%         \\&
        \leq 
        2 C_{\PF,{\rm EFNT},p}
        \volumeratio(\calT)^{\frac 1 p}
        \max\left( \diam(T_1), \diam(T_2) \right)
        \| \nabla u \|_{L^{p}(U)}
    \end{align*}
    for any $u \in W^{1,p}(\Omega)$ with $p \in [1,\infty]$.
\end{lemma}
% \begin{remark}
%     The result is sharp when $T_1$ and $T_2$ have equal volume and diameter, and that $U$ is not necessarily convex. 
% \end{remark}
\begin{proof}
    Without loss of generality, $F$ has the vertices $v_0, \dots, v_{n-1}$,
    and $z_{1} \in T_{1}$ and $z_{2} \in T_{2}$ are the remaining vertices of the two triangles. 
    Let $\Delta_{1} = \Delta^{n}$ be the reference $n$-simplex and let $\Delta_{2}$ be obtained from it by flipping the $n$-th coordinate.
    We let $\varphi_{1} : \Delta_{1} \rightarrow T_{1}$ and $\varphi_{2} : \Delta_{2} \rightarrow T_{2}$
    be affine transformations that map the $e_{i}$ to $v_{i}$ for $i = 0, \dots, n-1$ 
    and which satisfy $\varphi_{1}(e_{n}) = z_{1}$ and $\varphi_{2}(-e_{n}) = z_{2}$.
    Write $\hat U := \Delta_1 \cup \Delta_2$.
    We have a bi-Lipschitz mapping $\varphi : \hat U \rightarrow U$.

@@

%         \cdot \| \Jacobian \varphi_1 \|^{p}

@@

%         \cdot \| \Jacobian \varphi_2 \|^{p}

@@

%             |\det(\Jacobian \varphi_1)|^{-1} \cdot \| \Jacobian \varphi_1 \|^{p}

@@

%             |\det(\Jacobian \varphi_2)|^{-1} \cdot \| \Jacobian \varphi_2 \|^{p}

@@

            |\det(\Jacobian \varphi_1)|^{-\frac 1 p} \| \Jacobian \varphi_1 \|

@@

            |\det(\Jacobian \varphi_2)|^{-\frac 1 p} \| \Jacobian \varphi_2 \|

@@

    There exists $\hat w \in W^{1,p}(\hat U)$ such that $\nabla \hat w = \nabla \hat u$ and 

@@

    Let $T$ be an $n$-simplex with a face $F$. 

>>>>

\usepackage{comment}          % 
\usepackage{hyperref}         % For hypertext links
\usepackage{tikz-3dplot}      % 3d plots 
\usepackage{enumitem}
\setitemize[1]{left=0.0cm}

@@

\newcommand{\mwl}[1]{{\color{red} MWL: #1}}
\newcommand{\notice}[1]{{\color{red}REMARK: #1}}
\newcommand{\disk}{\cye{ball}}

@@

@@

Shellable triangulations are defined by a special constructive property:
we can assemble such triangulations sequentially, adding one simplex after another, such that the interface between the previous intermediate triangulation and the next simplex is always a boundary submanifold of both.
Loosely speaking, this guarantees that the interface with each successive simplex is sufficiently well-behaved.
Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler1995lectures}, which we only employ in a simple special case. 
In particular, local stars in 2D and 3D triangulations are shellable. 
\\

% This construction of potentials requires triangulations with special conditions: 
% we assemble the triangulation sequentially, adding one simplex after another, such that the interface between the previous intermediate triangulation and the next simplex is always a boundary submanifold of both.  Loosely speaking, this guarantees that the interface with each successive simplex is sufficiently well-behaved. Such triangulations are called \textit{shellable}. Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler1995lectures}, which we only employ in a simple special case. 
% In particular, local stars in 2D and 3D triangulations are shellable. 
% \\

@@

Whenever $\calT$ is a simplicial complex, 
the set of $k$-dimensional simplices in $\calT$ is denoted as $\subsimplex_{{k}}(\calT)$. 
% Additionally, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Edges(\calT) := \subsimplex_{1}(\calT)$ refer to the vertices and edges of the simplicial complex, respectively. In practice, we not always distinguish between points and singleton simplices. 
% Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces (that is, codimension one members) of this triangulation.\footnote{
Similarly, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ refer to the vertices and the faces (that is, codimension one members) of this triangulation.\footnote{
% \begin{remark}
    Our use of the term \textit{face} as is common in the finite element literature~\cite{brenner2008mathematical}
    and is synonymous with \textit{facet} as used in the literature on polyhedral combinatorics~\cite{schrijver1998theory}.
    Notably, this terminology differs from the uses \textit{face} and \textit{facet} in the theory of polyhedra~\cite{ziegler1995lectures}.
% \end{remark}
}
% Given $T \in \calT$, we let $\supsimplex(\calT,T)$ be the set of simplices in $\calT$ that contain $T$,
% and we write $\supsimplex_{k}(\calT,T)$ for the set of $k$-dimensional simplices in $\supsimplex(\calT,T)$.\footnote{\mwl{MWL: It might be more economical to get rid of the supersimplex set, it is only used in this section to define patches.}}

@@

Given a matrix $A \in \bbR^{n \times n}$, we let $\sigma_{1}(A) \geq \dots \geq \sigma_{n}(A) \geq 0$ denote the descending sequence of its singular values, 
where $\sigma_{\max}(A) := \sigma_{1}(A)$ is the largest and $\sigma_{\min}(A) := \sigma_{n}(A)$ is the smallest. 
We recall that the $\ell^{2}$ operator norm of $A$, written $\| A \|_{2}$, agrees with $\sigma_{\max}(A)$,
and if $A$ is invertible, then $\|A^{-1}\| = \sigma_{\min}(A)^{-1}$.
% Another norm on matrices, less common but useful for us, is the \emph{maximum column norm} $\|A\|_{\maxcol}$, which is defined as the largest $\ell^{2}$-norm of any column of $A$.

Whenever $T$ is any $n$-dimensional simplex $T$,
we define the \textit{geometric shape measure} $\geometricshapemeasure(T)$,
the \textit{aspect shape measure} $\aspectratio(T)$,
and 
the \textit{algebraic shape measure} $\algebraicshapemeasure(T)$
by 
\begin{align}\label{math:shapemeasure}
    \geometricshapemeasure(T)
    := 
    \frac{ \diam(T)^{n} }{ n! \vol(T) }
    ,
    \qquad 
    \aspectratio(T)
    := 
    \frac{ \diam(T) }{ \height(T) }
    ,
    \qquad 
    \algebraicshapemeasure(T)
    := 
    \sup_{ \varphi : \Delta^n \rightarrow T } 
    \frac{ \sigma_{\max}( \Jacobian \varphi ) }{ \sigma_{\min}( \Jacobian \varphi ) }
%     \sup_{ \varphi : \Delta^n \rightarrow T } \matnorm{\Jacobian \varphi}_{\maxcol} \matnorm{ \Jacobian \varphi^{-1} }_{\maxcol}
    ,
\end{align}
where the last supremum is taken over all affine transformation from the reference $n$-simplex onto the $n$-simplex $T$. 
% DONE: Although this is fairly clear upon reading, we could specify in word that $\geometricshapemeasure(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\volumeratio(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.

@@

We now gather a few relationships between geometric and algebraic entities and compare the different shape measures of a single simplex.

\begin{lemma}\label{lemma:measurerelationships}
    Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism from the reference $n$-simplex. Then 
    \begin{gather*}
        \matnorm{\Jacobian \varphi}
        \leq 
        \Ceins{n} \cdot \diam(T) % DONE: can this improved?
        ,
        \qquad 
        \matnorm{ \Jacobian \varphi^{-1} }
        \leq 
        \Czwei{n} \cdot 
        \geometricshapemeasure(T) 
        \diam(T)^{-1}
        ,
        \\
        \algebraicshapemeasure(T)
        \leq 
        \Cdrei{n}
        % \sqrt{ \frac{n}{ (n-1)^{n-1} } }
        \geometricshapemeasure(T)
        ,
        \qquad 
        %         \geometricshapemeasure(T)^{\frac 1 n}
        %         \leq 
        \aspectratio(T)
        \leq 
        \geometricshapemeasure(T)
        .
    \end{gather*}
    Here,
    \begin{align*}
        \Ceins{n} \leq \sqrt{n},
        \quad 
        \Czwei{n} \leq          \left( \frac{n-1}{n} \right)^{\frac{2}{n-1}}, 
        \quad 
        \Cdrei{n} \leq \Ceins{n}\Czwei{n} %\sqrt{n} \left( \frac{n}{n-1} \right)^{\frac{n-1}{2}}
        . 
    \end{align*}
\end{lemma}
\begin{proof}
%     The columns of the matrix $\Jacobian \varphi^{-1}$ are the gradients of the barycentric coordinates of the vertices of $T$,
%     except for the vertex $\varphi(0)$. It immediately follows that 
%     \begin{align*}
%         \matnorm{ \Jacobian \varphi^{-1} }_{2} \leq \sqrt{n} \cdot \height(T)^{-1}
%         .
%     \end{align*}
%     The smallest height in the reference simplex $\Delta^{n}$ is $1/\sqrt{n}$. 
%     
    We easily verify the first inequality. To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of the Jacobian $\Jacobian\varphi$ in descending order.
    The Jacobian determinant is the product of these singular values. 
    By a result of Hong and Pan \cite{hong1992lower},
    \begin{align*}
        \sigma_{n}
        &\geq 
        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
        \frac{ \det(\Jacobian\varphi) }{ \diam(T)^{n-1} }
        = 
        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
        \frac{ n! \vol(T) }{ \diam(T)^{n-1} }
        .
    \end{align*}
%     To get the second inequality, we multiple the last term by $\sigma_{1} / ( \sqrt{n} \diam(T) ) \leq 1$.
    The second inequality follows by taking the reciprocal. 
    The definition of the condition number now gives the third inequalities. 
    % To get the third inequality, we divide both sides by $\sigma_{1}$ and use $\sigma_{1} \leq \sqrt{n} \diam(T)$.
    Finally, 
    if $F$ is the face of $T$ opposite to the vertex with the smallest height, then 
    \begin{align*}
        \frac{ \diam(T) }{ \height(T) }
        \leq 
        \frac{ \diam(T) \vol(F) }{ n \vol(T) }
        \leq 
        \frac{ \diam(T)^{n} }{ n! \vol(T) }
        .
    \end{align*}
%     Since $n! \vol(T)$ is bounded from below by the product of any $n$ different heights of $T$, it follows that 
%     \begin{align*}
%         \frac{ \diam(T)^{n} }{ n! \vol(T) }
%         \leq 
%         \frac{ \diam(T)^{n} }{ \height(T)^{n} }
%         .
%     \end{align*}
    That shows the fourth and last of the inequalities. 
\end{proof}

@@

% Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^{n} / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
    % We can also rescale that by a factor of $1/n!$, as suggested from the above. 
    The geometric ratio $\geometricshapemeasure(T)$ equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}. 
    The \emph{thickness} of a simplex is the ratio of its smallest height to its diameter~\cite{munkres2016elementary}. \mwl{Update this entire paragraph.}
    Alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices.
    One example, commonly referenced in finite element literature, is the ratio of the diameter and the radius of the largest inscribed circle of a simplex 
% TODO     (see~\cite[p.61, Definition 5.1]{braess2001finite}, ~\cite[p.97, Definition (4.2.16)]{brenner2008mathematical},~\cite[Definition~11.2]{ern2021finite}). 
\end{remark}

We are interested in the maximal ratio of volumes between \mwl{face?} neighboring $n$-simplices, written $\volumeratio(\calT)$,
and the ratio of intersecting simplices, written $\diameterratio(\calT)$. Formally, 
\begin{align}
    \volumeratio(\calT) 
    := 
    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } 
    \frac{ \vol(T) }{ \vol(T') }
    ,
    \qquad 
    \diameterratio(\calT) 
    := 
    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \neq \emptyset } }
    \frac{ \diam(T) }{ \diam(T') }
    .
\end{align}
Finally, whenever $T, T'$ are two $n$-simplices that share a common face $F$ of codimension $1$, we let $\Xi_{T,T'} : T \rightarrow T'$ denote the affine diffeomorphism 
that preserves $F$. We then define 
\begin{align}\label{math:reflectionmeasure}
    \reflectionestimate(\calT) 
    := 
    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } }
    \matnorm{ \Jacobian \Xi_{T,T'} }
\end{align}
to be the maximum of the operator norm of the Jacobian of any such diffeomorphism. 
This indicator quantifies how much reflection across the shared face distorts the geometry.

@@

\begin{lemma}\label{lemma:volumecomparison}
    Let $T_1$ and $T_2$ be two $n$-simplices that share a common face $F$. Then 
    \begin{align*}
        \diam(T_1)
        \leq 
        % \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
        % \diam(F)
        % = 
        \geometricshapemeasure(T_1)
        \diam(F)
        ,
        \qquad 
        \frac{ \vol(T_1) }{ \vol(T_2) }
        \leq 
        % \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
        % \cdot 
        % \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
        % = 
        \aspectratio(T_1) \aspectratio(T_2)
        .
    \end{align*}
    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism that is the identity over $F$, then 
    \begin{align*}
        \matnorm{ \Jacobian \Xi }
        \leq 
        ( 1 + \aspectratio(T_2) ) \aspectratio(T_1)
        % \Cvier{n} \geometricshapemeasure(T_2) \geometricshapemeasure(T_1) 
        .
    \end{align*}
%     Here, $\Cvier{n} \leq \Ceins{n} \Czwei{n}$. 
\end{lemma}

@@

        \matnorm{ \Jacobian \Xi }
        \matnorm{ \Jacobian\phi_{2} } \cdot \matnorm{ \Jacobian\phi_{1}^{-1} }

@@

%         \matnorm{ \Jacobian \Xi }

@@

        \matnorm{ \Jacobian \Xi }

@@

\begin{remark}
    Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\rho(\calT)$ \cye{of~\eqref{math:volumecomparisonmeasure}} but not $\theta(\calT)$ \cye{of~\eqref{math:diametercomparison}}. 
    Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\volumeratio(\calT)$ but not $\diameterratio(\calT)$. 
    As seen above, we can bound the ratio of diameters and volumes of simplices that share at least one face in terms of the shape measure. 
    If we have an upper estimate for the number of simplices sharing a given vertex, 
    we can also bound the ratios of diameters and volumes of simplices sharing only a single common vertex. 
\end{remark}
%%%%%%%% END HERE

\mwl{Throughout the manuscript, use a macro for opnorm and equip the matrices with the operator norm index.}

@@

{\color{blue}In this section\cye{,} we \cye{develop a} stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains. \cye{The following very classical procedure serves us as an inspiration:} given a gradient vector field, we can reconstruct \cye{the scalar potential} up to a constant by fixing a starting point and integrating the gradient vector field along lines emanating from that starting point. 
Over triangulated domains, \cye{we fix} a starting triangle \cye{and perform this classical procedure. We then pass through the triangulation such that each subsequent simplex is connected to the previous ones by a face}. 
We always construct a gradient potential over the new simplex and fix the constant using the value already known on the connecting face.
This basic idea has appeared in the different variants before, for instance recently in \cite{Brae_Pill_Sch_p_rob_09, ern2020stable, Chaum_Voh_p_rob_3D_H_curl_24, Voh_loc_glob_H1_24}.
}

@@

{\color{blue}\cye{We start by extending the results on Poincar\'e--Friedrichs constants over convex domains from Section~\ref{section: PX_convex} to face patches within simplicial triangulations} in a way which captures the correct asymptotic behavior as $p$ grows to infinity. \cye{Let us stress that face patches are not necessarily convex and remark that our result is in particular sharp when $T_1$ and $T_2$ have similar volumes and diameters}.}

\begin{lemma}\label{lemma:poincarefriedrichsoverfacepatch}
    Let $\calT$ be a triangulation.
    Let $T_{1}, T_{2} \in \calT$ be two $n$-simplices whose intersection is a common facet $F := T_1 \cap T_2$. 
    Write $U := T_1 \cup T_2$. 
    Then 
    \begin{align*}
        \min\limits_{ c \in \bbR }
        \| u - c \|_{L^{p}(U)}
        &
%         \leq 
%         2 \Ceins{n} C_{\PF,{\rm EFNT},p}
%         \max\left( 
%             \frac{ \vol(T_1) }{ \vol(T_2) }
%             ,
%             \frac{ \vol(T_2) }{ \vol(T_1) }
%         \right)^{\frac 1 p}
%         \\&\qquad\qquad 
%         \cdot 
%         \max\left( \diam(T_1), \diam(T_2) \right)
%         \| \nabla u \|_{L^{p}(U)}
%         \\&
        \leq 
        2 \Ceins{n} C_{\PF,{\rm EFNT},p}
        \volumeratio(\calT)^{\frac 1 p}
        \max\left( \diam(T_1), \diam(T_2) \right)
        \| \nabla u \|_{L^{p}(U)}
    \end{align*}
    for any $u \in W^{1,p}(\Omega)$ with $p \in [1,\infty]$. \mwl{Introduce constant $C_{{\rm{PF}},T_1 \cup T_2,p}$}
\end{lemma}
% \begin{remark}
%     The result is sharp when $T_1$ and $T_2$ have equal volume and diameter, and that $U$ is not necessarily convex. 
% \end{remark}
\begin{proof}
    Without loss of generality, $F$ has the vertices $v_0, \dots, v_{n-1}$,
    and $z_{1} \in T_{1}$ and $z_{2} \in T_{2}$ are the remaining vertices of the two triangles. 
    Let $\Delta_{1} = \Delta^{n}$ be the reference $n$-simplex and let $\Delta_{2}$ be obtained from it by flipping the $n$-th coordinate.
    We let $\varphi_{1} : \Delta_{1} \rightarrow T_{1}$ and $\varphi_{2} : \Delta_{2} \rightarrow T_{2}$
    be affine transformations that map the $e_{i}$ to $v_{i}$ for $i = 0, \dots, n-1$ 
    and which satisfy $\varphi_{1}(e_{n}) = z_{1}$ and $\varphi_{2}(-e_{n}) = z_{2}$.
    Write $\hat U := \Delta_1 \cup \Delta_2$, which is (crucially) convex. .
    We have a bi-Lipschitz mapping $\varphi : \hat U \rightarrow U$.

@@

%         \cdot \matnorm{ \Jacobian \varphi_1 }^{p}

@@

%         \cdot \matnorm{ \Jacobian \varphi_2 }^{p}

@@

%             |\det(\Jacobian \varphi_1)|^{-1} \cdot \matnorm{ \Jacobian \varphi_1 }^{p}

@@

%             |\det(\Jacobian \varphi_2)|^{-1} \cdot \matnorm{ \Jacobian \varphi_2 }^{p}

@@

            |\det(\Jacobian \varphi_1)|^{-\frac 1 p} \matnorm{ \Jacobian \varphi_1 }

@@

            |\det(\Jacobian \varphi_2)|^{-\frac 1 p} \matnorm{ \Jacobian \varphi_2 }

@@

    Thus, due to~\eqref{math:esposito:pf}, there exists $\hat w \in W^{1,p}(\hat U)$ such that $\nabla \hat w = \nabla \hat u$ and 

@@

    Let $T$ be an $n$-simplex with a face $F$ and $p \in [1,\infty]$. 
